Fall Detection in Video Sequences Based on a \\ Three-Stream Convolutional Neural Network

### 2019-11-28 2019_ICMLA/paper.tex
Updates from Overleaf

\begin{table*}[!htb]
\centering
\caption{Comparison of the results on URFD datasets (descending order of accuracy).}
\label{tab:urfd-our-their}
\begin{tabular}{llcccl}
\hline
 &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
 & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
 & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
 & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & \textbf{98.61}    & 98.77             & \\
 & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
 & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
 & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
 & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
 & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
 & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
 & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
 & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
\end{tabular}
\end{table*}

@@

\begin{table*}[!htb]
\centering
\caption{Comparison of the results on FDD dataset (descending order of accuracy).}
\label{tab:fdd-our-their}
\begin{tabular}{llcccl}
\hline
 &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
 & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
 & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
 & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
 & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & \textbf{98.32}    & 98.43             & \\
 & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
 & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
 & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
 & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
\end{tabular}
\end{table*}

@@

It is worth discussing the selected features and some literature results. As et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity. Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.

>>>>

\begin{table*}[!htb]
\centering
\caption{Comparison of the results on URFD datasets (descending order of accuracy).}
\label{tab:urfd-our-their}
\begin{tabular}{llcccl}
\hline
 &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
 & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
 & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
 & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & 98.61    & 98.77             & \\
 & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
 & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
 & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
 & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 91.00              & 96.00             & \\
 & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
 & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
 & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
 & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
\end{tabular}
\end{table*}

@@

\begin{table*}[!htb]
\centering
\caption{Comparison of the results on FDD dataset (descending order of accuracy).}
\label{tab:fdd-our-their}
\begin{tabular}{llcccl}
\hline
 &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
 & Ours                                                 & 99.43    & 99.55             & \textbf{99.51}    & \\
 & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
 & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
 & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & 98.32    & 98.43             & \\
 & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
 & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
 & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
 & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
\end{tabular}
\end{table*}

@@

It is worth discussing the selected features and some literature results. As Chernbumroong et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity. Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
